\begin{rubric}{Science Outreach}

\subrubric{Organizational role}
\entry*[Jan 2021-] \textbf{Research Assistant}, ABEx Bio-Research Center, Dhaka 1230, Bangladesh.
%
\entry*[Mar 2020 -] \textbf{Project Mentor,}  Bio-Science Research Initiative, Gopalganj 8100, Bangladesh.
%
\entry*[Jan 2018 -] \textbf{Research Assistant,}  Evergreen Scientific Research Centre, Gopalganj 8100, Bangladesh.
%%%%%%%%%%%%%%%%%%%%%%
\subrubric{Training}
%%%%%%%%%%%%%%%%%%%%%%
\entry*[Mar 29, 2020] \textbf{}Training on CRISPR Cas-9 molecular biology tool conducted by Bio Bangla and Dept. of BMB, BSMRSTU, Gopalganj 8100 Bangladesh.
%
\entry*[Mar 08, 2019] \textbf{}Hands-on Training Workshop on Molecular Biological Tools used for DNA Barcoding and Basic Bioinformatics at Molecular Pathology Lab of CVASU, Chittagong 4225, Bangladesh.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subrubric{Workshops}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\entry*[Apr 22, 2018] \textbf{}A journey to code and sequence 02 at BSMRSTU, Gopalganj 8100, Bangladesh.
%
\entry*[Apr 06, 2018] \textbf{}Code and sequence returns at BSMRSTU, Gopalganj 8100, Bangladesh.
%
\entry*[Feb 10, 2018] \textbf{}Training on bioinformatics at Rajshahi University, Rajshahi, Bangladesh.
%
\entry*[Jan 02, 2018] \textbf{}A journey to code and sequence (workshop) at BSMRSTU, Gopalganj 8100, Bangladesh.
%
\entry*[Oct 29, 2017] \textbf{}Workshop on Computational Chemistry at Red green research center Dhaka, Bangladesh.
%
\entry*[Sep 11, 2017] \textbf{}A Workshop on Synthetic Biology by Bio Bangla at NMST, Dhaka, Bangladesh.
%
\entry*[Aug 06, 2017] \textbf{}Workshop on Synthetic Biology by Bio Bangla at Software Technology Park, Dhaka, Bangladesh.
%
\entry*[Apr 11, 2017] \textbf{}Advance workshop on computational chemistry at Red Green Research Center Dhaka, Bangladesh.

\end{rubric}